%!TEX program = xelatex
\documentclass[10pt,a4paper]{article}

% Base packages
\usepackage[left=1.0cm, right=1.0cm, top=0.8cm, bottom=0.8cm]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{hyperref}

% Color definitions
\definecolor{titlecolor}{RGB}{0, 102, 204}
\definecolor{sectioncolor}{RGB}{51, 51, 51}

% Hyperlink settings
\hypersetup{
    colorlinks=true,
    linkcolor=titlecolor,
    urlcolor=titlecolor,
    pdfauthor={Kyle Xu},
    pdftitle={Kyle Xu - Resume}
}

% Paragraph settings
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlength{\lineskip}{0pt}
\setlength{\baselineskip}{10pt}
\pagestyle{empty}

% Custom commands
\newcommand{\name}[1]{
    \begin{center}
        {\LARGE\bfseries\color{titlecolor} #1}
    \end{center}
    \vspace{2pt}
}

\newcommand{\contactinfo}[4]{
    \begin{center}
        {\small #1 \quad | \quad #2 \quad | \quad #3 \quad | \quad #4}
    \end{center}
    \vspace{3pt}
}

\newcommand{\sectiontitle}[1]{
    \vspace{5pt}
    {\large\bfseries\color{sectioncolor} #1}
    \vspace{1pt}
    \hrule height 0.8pt
    \vspace{5pt}
}

\newcommand{\jobentry}[5]{
    \vspace{5pt}
    \textbf{#1} \hfill #2 \hfill \textit{#3}\\
    #5
    \vspace{2pt}
}

\newcommand{\projectentry}[3]{
    \vspace{5pt}
    {\large\textbf{#1}}
    \vspace{2pt}
    {\small\textit{#2}}
    \vspace{2pt}
    #3
    \vspace{5pt}
}

\begin{document}

% Name
\name{Kyle Xu (Zhongjian Xu)}

% Contact Information
\contactinfo{
    \href{mailto:zjxu97@gmail.com}{zjxu97@gmail.com}
}{
    +86 18971672214
}{
    \href{https://linkedin.com/in/xu-kyle}{linkedin.com/in/xu-kyle}
}{
    Senior Backend Engineer (6 Years of Experience)
}

% Education
\sectiontitle{Education}

\textbf{Heilongjiang University} \hfill \textit{Sep 2016 - Jun 2020}\\
Bachelor of Engineering in Electronic Information Engineering

% Work Experience
\sectiontitle{Work Experience}

\jobentry{Tiger Brokers · Crypto Exchange · Post-Trade Team}{Senior Software Engineer}{May 2023 - Present}{Beijing}{
Hong Kong licensed cryptocurrency exchange. Responsible for the design, development, and maintenance of market data systems, OTC business, and rule engine platform.
}

\jobentry{Meituan · In-Store Business Group · Hotel Division · Distribution Team}{Software Engineer}{May 2021 - Mar 2023}{Beijing}{
Responsible for the development and maintenance of hotel distributor management system, implementing API rate limiting and signature verification systems.
}

\jobentry{Xiaomi · China Region · New Retail Business · System Development Team}{Software Engineer}{Oct 2019 - Apr 2021}{Beijing}{
Participated in new retail business system development and optimization, responsible for order system and inventory management modules.
}

% Core Project Experience
\sectiontitle{Core Project Experience}

\projectentry{Rule Engine Platform \textit{@Tiger Brokers}}{Flink, Spring Boot, Kafka, Redis, MySQL, REST API}{
\begin{itemize}[leftmargin=0.8em, itemsep=1pt, parsep=0pt, topsep=0pt]
    \item \textbf{Background}: Built a unified processing platform supporting dynamic task configuration and rule engine for \textbf{risk control, account opening, KYC} and other business scenarios.
    \item \textbf{Platform Architecture}: Designed multi-source data ingestion architecture, unified streaming and batch task processing, supporting Kafka and MySQL as data sources.
    \item \textbf{Configuration Management}: Implemented end-to-end configuration from data source input, processing logic, to output, enabling zero-code rapid deployment for business teams.
    \item \textbf{Dynamic Rule Engine}: Supported Flink SQL dynamic rule submission, online editing and hot-reloading, reducing rule loading time by \textbf{90\%}.
    \item \textbf{Efficiency Improvement}: Reduced task deployment cycle from 1 day to 1 hour, supporting real-time computing requirements across multiple business lines.
\end{itemize}
}

\projectentry{Market Data System \textit{@Tiger Brokers}}{Flink, Kafka, Redis, DynamoDB, WebSocket, MQTT, Thrift}{
\begin{itemize}[leftmargin=0.8em, itemsep=1pt, parsep=0pt, topsep=0pt]
    \item \textbf{Background}: Built a unified market data platform integrating internal matching engine and external exchange data, providing real-time data services for trading, risk control, and frontend.
    \item \textbf{Internal Market Calculation}: Connected to matching engine trade stream, implemented real-time K-line calculation using Flink sliding windows, supporting depth, volume, and other indicator aggregations.
    \item \textbf{External Market Integration}: Real-time subscription to major exchanges (Binance, Crypto.com) via WebSocket, implementing data standardization and caching.
    \item \textbf{Tiered Storage}: Redis for hot data + DynamoDB for historical market data persistence, meeting real-time query and regulatory reporting requirements.
    \item \textbf{Risk Monitoring}: Real-time monitoring of abnormal price fluctuations, large transactions, and liquidity depletion events, triggering alerts and automatic failover to backup data sources.
\end{itemize}
}

\projectentry{OTC Trading System \textit{@Tiger Brokers}}{Spring Boot, Redis, MySQL, XXL-Job, State Machine, Thrift, RateLimiter}{
\begin{itemize}[leftmargin=0.8em, itemsep=1pt, parsep=0pt, topsep=0pt]
    \item \textbf{Background}: Built an OTC trading system for fiat and cryptocurrency, supporting large-volume exchanges between users and LPs (Liquidity Providers).
    \item \textbf{Price Management}: Maintained proprietary order book, supporting multi-LP API and Socket dual-channel quoting, aggregation algorithm for optimal pricing.
    \item \textbf{Order State Machine}: Designed complete order lifecycle (Quote→Lock→Trade→Settlement→Confirmation), covering asset locking and fund transfers.
    \item \textbf{Risk Control System}: Real-time user risk scoring based on Flink, combining account information and trading behavior for multi-dimensional risk control.
    \item \textbf{Net Settlement Optimization}: Aggregated unsettled orders for net settlement, reducing transfer frequency, improving capital turnover rate by \textbf{70\%}.
\end{itemize}
}

\projectentry{Distributor Management System \textit{@Meituan}}{Spring, Redis, MySQL, XXL-Job, Thrift, State Machine, Guava Cache, MyBatis}{
\begin{itemize}[leftmargin=0.8em, itemsep=1pt, parsep=0pt, topsep=0pt]
    \item \textbf{Background}: Provided hotel and ticket distribution services across industries, managing full distributor lifecycle.
    \item \textbf{Rate Limiting System}: Implemented merchant-level traffic limiting based on Redis + Guava Cache, preventing malicious requests and system overload.
    \item \textbf{Signature Verification}: Redis for signature storage combined with Guava Cache for improved verification efficiency, QPS improved by \textbf{3x}.
    \item \textbf{Lifecycle Management}: State Machine managing distributor status transitions (Application→Review→Active→Suspended→Offline), preventing illegal state transitions.
    \item \textbf{Merchant Profiling}: Processed merchant tracking data, built profiling system supporting precision operations.
    \item \textbf{Rate Limiting}: Sliding window rate limiting algorithm (Redis + Lua script); multi-level cache architecture (Guava Cache + Redis) reducing database pressure.
\end{itemize}
}

% Professional Skills
\sectiontitle{Professional Skills}

\begin{itemize}[leftmargin=0.8em, itemsep=3pt, parsep=0pt, topsep=0pt]
    \item \textbf{Programming \& Frameworks}: Proficient in Java, familiar with Python and SQL; skilled in Spring Boot, MyBatis and other backend frameworks.
    \item \textbf{Middleware \& Storage}: Deep expertise in Flink real-time computing, Kafka messaging, Redis caching, MySQL, DynamoDB, Thrift RPC, etc.
    \item \textbf{Architecture \& DevOps}: Experienced in microservices architecture, high-concurrency system design, DDD domain modeling, state machine design; familiar with Docker, Kubernetes, Prometheus, Grafana.
    \item \textbf{Real-time Computing \& High-Concurrency}: Deep expertise in Flink stream processing, skilled in designing distributed systems with 10k+ concurrency and sub-second latency, familiar with multi-level caching and rate limiting architectures.
    \item \textbf{Complex Business System Design}: Extensive experience in trading, settlement, and risk control financial system design, skilled in complex business abstraction and state machine modeling, capable of independent 0-to-1 architecture design.
    \item \textbf{Platform Infrastructure}: Built configurable, reusable rule engine and task scheduling platforms, enabling rapid business iteration, reducing task deployment cycle from days to hours.
\end{itemize}

\end{document}
